Model 

### 2019-10-03 04_estimation.Rmd
Add lagged physical activity to obesity models

```{r lagged_vars}
contiglagged_vars <- tracts_access %>%
  st_set_geometry(NULL) %>%
  as_tibble() %>%
  transmute_at(
    vars(density, income, fulltime, college, single, youth, young_adults, seniors, black, asian, hispanic, other),
    ~lag.listw(Wcontig, .)
  ) %>%
  mutate(geoid = tracts_access$geoid) %>%
  dplyr::select(geoid, everything())

@@

```{r obesity_models}
obesity_models <- lapply(pa_models, function(model){
  update(update(model, obesity ~ . + physact))
})

>>>>

```{r lagged_vars}
contiglagged_vars <- tracts_access %>%
  st_set_geometry(NULL) %>%
  as_tibble() %>%
  transmute_at(
    vars(density, income, fulltime, college, single, youth, young_adults, seniors, black, asian, hispanic, other, physact),
    ~lag.listw(Wcontig, .)
  ) %>%
  mutate(geoid = tracts_access$geoid) %>%
  dplyr::select(geoid, everything())

@@

```{r obesity_models}
obesity_models <- lapply(pa_models, function(model){
  update(update(model, obesity ~ . + physact + lag.physact))
})
